Reanalysis Step 5: Outcome Analysis with Three-Way Interaction

### 2025-09-01 reanalysis-5-outcome_analysis-interaction.qmd
caching on ix model

@@

```{r fit-models}
models <- list()
model_summaries <- list()

@@

@@

@@

@@

@@

>>>>

# CACHE SETTINGS - Set these to TRUE to force recalculation
force_refit_models <- FALSE  # Set to TRUE to re-fit all models
force_recalc_emmeans <- FALSE  # Set to TRUE to recalculate marginal means
force_recalc_ame <- FALSE  # Set to TRUE to recalculate AMEs with marginaleffects

@@

```{r fit-models}
# Check if models are already cached
models_cache_file <- file.path(reanalysis_data_dir, "fitted_models_interaction.rds")

if (file.exists(models_cache_file) && !force_refit_models) {
  # Load cached models
  cached_models <- readRDS(models_cache_file)
  models <- cached_models$models
  model_summaries <- cached_models$model_summaries
  model_progress <- cached_models$model_progress
  models_loaded_from_cache <- TRUE
  cache_location <- models_cache_file
  message("Models loaded from cache: ", cache_location)
} else {
  # Fit new models
  models_loaded_from_cache <- FALSE
  models <- list()
  model_summaries <- list()

@@

  # Save to cache
  cached_models <- list(
    models = models,
    model_summaries = model_summaries,
    model_progress = model_progress,
    formula_used = interaction_formula,
    n_imputations = n_imputations,
    timestamp = Sys.time()
  )

  saveRDS(cached_models, models_cache_file)
  cache_location <- models_cache_file
  message("Models fitted and saved to cache: ", cache_location)
}

@@

# Check if emmeans results are cached
emmeans_cache_file <- file.path(reanalysis_data_dir, "emmeans_results_interaction.rds")

if (file.exists(emmeans_cache_file) && !force_recalc_emmeans) {
  # Load cached results
  pooled_results <- readRDS(emmeans_cache_file)
  emmeans_loaded_from_cache <- TRUE
  emmeans_cache_location <- emmeans_cache_file
  message("Emmeans results loaded from cache: ", emmeans_cache_location)
} else {
  # Calculate new emmeans results
  emmeans_loaded_from_cache <- FALSE

@@

  # Save to cache
  saveRDS(pooled_results, emmeans_cache_file)
  emmeans_cache_location <- emmeans_cache_file
  message("Emmeans results calculated and saved to cache: ", emmeans_cache_location)
}

@@

# Check if AME results are cached
ame_cache_file <- file.path(reanalysis_data_dir, "ame_results_interaction.rds")

if (file.exists(ame_cache_file) && !force_recalc_ame) {
  # Load cached results
  ame_results <- readRDS(ame_cache_file)
  ame_loaded_from_cache <- TRUE
  ame_cache_location <- ame_cache_file
  message("AME results loaded from cache: ", ame_cache_location)
} else {
  # Calculate new AME results
  ame_loaded_from_cache <- FALSE

@@

  # Save to cache
  saveRDS(ame_results, ame_cache_file)
  ame_cache_location <- ame_cache_file
  message("AME results calculated and saved to cache: ", ame_cache_location)
}
